```{r}
# install.packages('tidyverse')
# install.packages('lubridate')
# install.packages('plotly')
# install.packages('janitor')
# install.packages('yaml')
```
---
title: "Carbon Emissions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(plotly)
library(janitor)

# read in data
footprint <- read_csv("NFA 2018.csv") %>%
    clean_names()
    
## Data preparation
per_year_country <- footprint %>%
    group_by(year, country) %>%
    summarise(total_carbon = sum(carbon, na.rm = T), total_land=sum(total, na.rm = T), population=max(population), GDP=mean(percapita_gdp_2010_usd), continent=first(un_region)) %>%
    na.omit()

per_year_continent <- per_year_country %>%
    group_by(year, continent) %>%
    summarise(total_carbon = sum(total_carbon, na.rm = T), population = sum(population)) %>%
    na.omit()
```

---

In the following graph we can see the Yearly Carbon Emissions per Continent


```{r, echo=FALSE}
(ggplot(per_year_continent %>% filter(continent != 'World'), aes(year, total_carbon)) + geom_area(aes(fill=continent), alpha=0.5) + ylab('Total Carbon Emissions') + ggtitle('Yearly Carbon Emissions per Continent')) %>%
ggplotly()


```

---

The next graph shows Worldwide Yearly Carbon Emissions


```{r, echo=FALSE}

plot_ly(per_year_continent %>% filter(continent=='World'), 
        x = ~year,
        y = ~total_carbon, 
        type = 'scatter', 
        mode = 'line') %>%
layout(title='World Carbon Emissions per Year', yaxis = list(title=""))

```

---

Let's suppose we would like to see how Carbon Emissions are affected by Total Land and Population of a country.
The size of the markers in the following graph indicates the value of Carbon Emissions


```{r, echo=FALSE}

p <- ggplot(per_year_country %>% filter(continent!='World'), aes(total_land, population)) + geom_point(aes(size=total_carbon, , color=continent), alpha=0.5) + 
    labs(title='Carbon Emissions related to Total Land and Population', subtitle = '(size of marker indicates value of emissions)')
ggplotly(p)

```

---

Finally, here is a map of the mean carbon emissions per country

```{r, echo=FALSE}

mean_carbon_per_country <- per_year_country %>%
    group_by(country) %>%
    summarize(mean_carbon = mean(total_carbon, na.rm = T))

# specify some map projection/options
g <- list(
  scope = 'world',
  projection = list(type = 'natural earth'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

# create our plot
plot_geo(mean_carbon_per_country, locationmode = 'country names') %>%
  add_trace(
    z = ~mean_carbon, 
    locations = ~country,
    color = ~mean_carbon,
    colors = "Reds"   
  ) %>%
  layout(
    title = 'Mean Carbon Emissions per Country',
    geo = g
  )

```